Model

### 2019-04-20 stats/model.Rmd

    return extend([
      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
    ])

@@

>>>>

    return {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 5, burn = 1, verbose = T)
)
